r5r: rapid realistic routing on multimodal transport networks with R5 in R

### 2020-10-22 r-package/paper2020/paper2020.Rmd
fixes paper detailed itineraries example

- `travel_time_matrix()`: computes travel time estimates between one or 
multiple origin/destination pairs for a single departure time or for multiple
departure times over a time window. This function uses an R5-specific extension to the RAPTOR routing algorithm developed by Conway et al. [@conway2017evidencebased], which provides an efficient and systematic sample of 
multiple departures per minute over a `time_window` set by the user. If the user
passes a `time_window` parameter to the function, r5r will calculate multiple travel 
time matrices departing each minute and return additional information on the percentile distribution of travel times that allows one to grasp service reliability issues.

- `detailed_itineraries()`: computes detailed information on either the
shortest or multiple alternative routes between one or multiple origin/destination
pairs for a single departure time. The output includes detailed information on
route alternatives such as the transport mode, waiting time, travel time and 
distance of each segment of the trip. This function uses an R5-specific extension
to the McRAPTOR routing algorithm to find paths that are optimal or less than
optimal. The specific extension to McRAPTOR to do suboptimal path routing are not documented yet, but a detailed description of base McRAPTOR can be found in @delling2015roundbased.

@@

Often enough one wants more information on the itineraries between 
origin/destination pairs than simply the travel time. For such cases, the 
package includes the `detailed_itineraries()` function, which also takes travel 
restrictions as inputs, but outputs a much more detailed data set at the trip 
segment level. Another key feature of this function is that it (optionally) 
provides multiple alternative routes between origin/destination pairs:

@@

The picture above can be used to compare the walking-only to the walking and 
transit itineraries between each origin/destination pair. Given that the sample 
`GTFS.zip` file includes only very few public transport routes, the resulting 
plot picture some odd scenarios, such as a fairly lengthy circular-like bus 
route, in the leftmost facet, and a very long walking access trip to the bus, 
in the rightmost facet.

>>>>

- `travel_time_matrix()`: computes travel time estimates between one or 
multiple origin/destination pairs for a single departure time or for multiple
departure times over a time window. This function uses an R5-specific extension 
to the RAPTOR routing algorithm which provides an efficient and systematic 
sample of multiple departures per minute over a `time_window` set by the user 
[@conway2017evidencebased]. If the user passes a `time_window` parameter to the 
function, r5r calculates multiple travel time matrices departing each minute and 
return additional information on the percentile distribution of travel times 
that allows one to grasp service reliability issues.

- `detailed_itineraries()`: computes detailed information on either the
shortest or multiple alternative routes between one or multiple origin/destination
pairs for a single departure time. The output includes detailed information on
route alternatives such as the transport mode, waiting time, travel time and 
distance of each segment of the trip. This function uses an R5-specific 
extension to the McRAPTOR routing algorithm to find optimal or less than optimal 
paths. The specific extension to McRAPTOR to do suboptimal path routing are not 
documented yet, but a detailed description of base McRAPTOR can be found in 
@delling2015roundbased.

@@

Often enough one wants more information on the itineraries between 
origin/destination pairs than simply the travel time. For such cases, the 
package includes the `detailed_itineraries()` function, which also takes travel 
restrictions as inputs, but outputs a much more detailed data table at the trip 
segment level. Another key feature of this function is that it (optionally) 
provides multiple alternative routes between origin/destination pairs. The 
algorithm doesn't yet support frequency-based trips (such as São Paulo's), 
however, so we use another data sample included in the package that covers the 
city of Porto Alegre (Brazil):

@@

The picture above can be used to compare the walking-only to the walking and 
transit itineraries between each origin/destination pair. Given that Porto 
Alegre's sample `GTFS.zip` file includes only very few public transport routes, 
the resulting plot picture some odd scenarios, such as a fairly lengthy 
circular-like bus route, in the leftmost facet, and a very long walking access 
trip to the bus, in the rightmost facet.
